|

### 2024-08-08 doc/paper.qmd
update

def prep_latex_table(df, caption=None, label=None):
    df = escape_underscores(df.reset_index())
    num_columns = len(df.columns)
    column_format = 'l' + 'r' * (num_columns - 1)
    latex_table = df.to_latex(
        column_format=column_format,
        index=False,
        float_format=custom_float_format,
    )
    latex_table_lines = [
        "\\begin{table}[htbp]",
        "\\centering",
        "\\resizebox{\\textwidth}{!}{%",
        latex_table,
        "}",
        f"\\caption{{{caption}}}" if caption else "",
        f"\\label{{{label}}}" if label else "",
        "\\end{table}"
    ]
    return "\n".join(line for line in latex_table_lines if line)
```

@@

Now that it is clear that the number of observations for this project is significantly higher than that in @Leuz_2003 study, in order to illustrate the differences and compare the firm-year observations, Table 1 from @Leuz_2003 was partially replicated (only columns on countries and firm/year observations) to distinguish specific discrepancies that could arise for certain countries. The following table representes the (partially) replicated Table 1.

print(prep_latex_table(
    results['table_1'],
    caption='Table 1: Number of Firm-Year Observations per Country',
    label='tab:table_1'
))
```

>>>>

def prep_latex_table(df, caption=None, label=None, fontsize='\\fontsize{11}{13}\\selectfont'):
    df = escape_special_characters(df.reset_index())
    num_columns = len(df.columns)
    column_format = 'l' + 'r' * (num_columns - 1)
    latex_table = df.to_latex(
        column_format=column_format,
        index=False,
        float_format=custom_float_format,
    )
    latex_table_lines = [
        "\\begin{table}[htbp]",
        "\\centering",
        fontsize,  # Set font size for the table
        latex_table,
        f"\\caption{{{caption}}}" if caption else "",
        f"\\label{{{label}}}" if label else "",
        "\\end{table}"
    ]
    return "\n".join(line for line in latex_table_lines if line)
```

@@

Now that it is clear that the number of observations for this project is significantly higher than that in @Leuz_2003 study, in order to illustrate the differences and compare the firm-year observations, Table 1 from @Leuz_2003 was partially replicated (only columns on countries and firm/year observations) to distinguish specific discrepancies that could arise for certain countries. The following representes the (partially) replicated Table 1.

```{python}
#| label: table_1 
#| echo: false
#| output: asis

print(prep_latex_table(
    results['table_1'],
    caption='Number of Firm-Year Observations per Country',
    label='tab:table_1'
))
```
